Title Text

### 2011-06-12 talk/iwtc11/paper.tex
implementation detail

Note that virtuals are only exploded into their attributes when
constructing the arguments of the jump of the first iteration. This
explosion can't be repeated when constructing the arguments of the
jump of the second iteration as it has to mach the first. This means
the objects that was passed as pointers (non virtuals) from the first
iteration to the second also has to be passed as pointers from the
second iteration to the third. If one of these objects are virtual
at the end of the second iteration they need to be allocated right
before the jump.

>>>>

Note that virtuals are only exploded into their attributes when
constructing the arguments of the jump of the first iteration. This
explosion can't be repeated when constructing the arguments of the
jump of the second iteration as it has to mach the first. This means
the objects that was passed as pointers (non virtuals) from the first
iteration to the second also has to be passed as pointers from the
second iteration to the third. If one of these objects are virtual
at the end of the second iteration they need to be allocated right
before the jump. With the simple objects considered in this paper,
that is not a problem. However in more complicated interpreters such
an allocation might, in combination with other optimizations, lead
to additional variables from the first iteration being imported into
the second. This extends both $\hat J$ and $\hat K$, which means that
some care has to be taken, when implementing this, to allow $\hat J$ to
grow while inlining it into $\hat K$.
